%% Gianluca Covini -- Academic CV for webpage
%% Revised version: cleaner academic structure, more selective coursework, corrected wording

\documentclass[11pt,a4paper,sans]{moderncv}

% moderncv themes
\moderncvstyle{classic}
\moderncvcolor{blue}

\definecolor{cvtext}{HTML}{263B4A}
\definecolor{cvsection}{HTML}{174F73}
\definecolor{cvaccent}{HTML}{2878A8}
\definecolor{cvsecondary}{HTML}{527386}
\definecolor{cvline}{HTML}{A9BDC8}

\colorlet{color0}{cvtext}
\colorlet{color1}{cvsection}
\colorlet{color2}{cvsecondary}

% Colour actually used by moderncv for section bars
\colorlet{bodyrulecolor}{cvsection}

\newcommand{\cvsubsection}[1]{%
  \par
  \vspace{0.9em}%
  \noindent
  {\large\bfseries\color{cvaccent}#1}%
  \par
  \vspace{0.15em}%
  \noindent
  {\color{cvline}\rule{\textwidth}{0.4pt}}%
  \par
  \vspace{0.7em}%
}



% School without a description
% #1 year, #2 month, #3 title, #4 institution/location
\newcommand{\school}[4]{%
  \cvitem[0.05em]{#1}{%
    \hangindent=3.2em%
    \hangafter=1%
    \makebox[3.2em][l]{\textbf{#2}}%
    \textbf{#3}, \emph{#4}.%
  }%
}

% School with a short description
% #1 year, #2 month, #3 title, #4 institution/location, #5 topics
\newcommand{\schoolwithtopics}[5]{%
  \cvitem[0.05em]{#1}{%
    \hangindent=3.2em%
    \hangafter=1%
    \makebox[3.2em][l]{\textbf{#2}}%
    \textbf{#3}, \emph{#4}. #5%
  }%
}

% page layout
\usepackage[scale=0.75]{geometry}
\setlength{\hintscolumnwidth}{3cm}

\usepackage{iftex}

% fonts / encoding
\ifxetexorluatex
  \usepackage{fontspec}
  \usepackage{unicode-math}
  \defaultfontfeatures{Ligatures=TeX}
  \setmainfont{Latin Modern Roman}
  \setsansfont{Latin Modern Sans}
  \setmonofont{Latin Modern Mono}
  \setmathfont{Latin Modern Math}
\else
  \usepackage[T1]{fontenc}
  \usepackage{lmodern}
\fi

% language
\usepackage[english]{babel}

% timelines
\usepackage[firstyear=2018,lastyear=2030]{moderntimeline}
\tlmaxdates{2019}{2030}

% links
\usepackage[hidelinks]{hyperref}

% personal data
\name{Gianluca}{Covini}
\title{%
  {\large PhD Student in Statistics and Computer Science}\\[-0.1em]
  {\normalsize Bocconi University}%
}

% For web privacy, keep address and phone commented out.
%\address{}{Milan, Italy}{}
% \phone[mobile]{+39~366~486~3333}

\homepage{gianlucacovini.github.io}
\social[github]{gianlucacovini}
\email{gianluca.covini@phd.unibocconi.it}
% \social[linkedin]{gianluca-covini}

% \photo[64pt][0.4pt]{GianCv}
% \quote{My current research interests lie in \textbf{optimal transport}, with a focus on \emph{entropic OT, Sinkhorn-type geometries and gradient-flow perspectives}, motivated by applications in statistics, optimization, and machine learning.}

\renewcommand*{\bibliographyitemlabel}{[\arabic{enumiv}]}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
\color{cvtext}
\makecvtitle

%----------------------------------------------------------------------------------
% Research interests
%----------------------------------------------------------------------------------

%----------------------------------------------------------------------------------
% Education
%----------------------------------------------------------------------------------
\section{Academic Background}

\cvsubsection{Education}

\tlcventry{2025/9}{2030/1}%
        {\href{https://www.unibocconi.it/en/programs/phd/phd-statistics-and-computer-science}{PhD in Statistics and Computer Science}}%
        {Bocconi University}%
        {Milan, Italy}%
        {}%
        {\begin{itemize}
        \item \textbf{Advisor:} Prof. Hugo Lavenant.
        \item \textbf{Current research topics:} entropic optimal transport, variational methods.
        \item \textbf{Selected PhD coursework} (\emph{GPA: A}): Measure Theory and Optimal Transport; Probability Theory and Stochastic Processes; Statistical Theory; Theoretical Computer Science and Programming.
        \end{itemize}}

\tlcventry{2022/9}{2025/2}%
        {\href{https://matematica.unipv.it/didattica/corsi-di-laurea/laurea-magistrale-in-matematica/}{MSc in Mathematics}}%
        {University of Pavia}%
        {Pavia, Italy}%
        {\textit{110/110 \emph{cum laude}; GPA: 29.5/30}}%
        {\begin{itemize}
          \item \textbf{Selected coursework:} Functional Analysis; Advanced Probability; Stochastic Processes; Foundations of Geometry; Mathematical Finance; Econometrics; Machine Learning; Finite Element Method; Dynamical Systems.
          \item \textbf{Additional coursework attended beyond the curriculum:} Advanced Functional Analysis; Evolution Equations; Calculus of Variations.
          \item \textbf{Master's thesis:} \emph{Dynamic Parameter Policies for LeadingOnes on Enhanced State Spaces}, supervised by Prof. Carola Doerr (Sorbonne Universit\'e/CNRS) and Prof. Stefano Gualandi (University of Pavia).
        \end{itemize}}

\tlcventry{2022/9}{2024/7}%
        {Student of the Merit-Based Programme}%
        {\href{https://www.collegioborromeo.it/}{Almo Collegio Borromeo}}%
        {Pavia, Italy}%
        {}%
        {\begin{itemize}
          \item \textbf{Courses attended:} Optimal Transport for Optimization; Fuzzy Logic; Introduction to Stochastic Differential Equations; Quantitative Methods for Art.
          \item \textbf{Co-organized courses:} Machine Learning for Healthcare Management; Seminar Series in Mathematics.
          \item \textbf{Reading groups:} Hausdorff Measure and Fractals; Laplacian Eigenvalues, supervised by Prof. Dario Mazzoleni.
        \end{itemize}}

\tlcventry{2019/10}{2022/9}%
        {\href{https://matematica.unipv.it/laurea-in-matematica/}{BSc in Mathematics}}%
        {University of Pavia}%
        {Pavia, Italy}%
        {\textit{110/110 \emph{cum laude}; GPA: 29.8/30}}%
        {\begin{itemize}
          \item \textbf{Selected coursework:} Mathematical Analysis; Linear Algebra; Algebra; Geometry; Probability; Mathematical Statistics; Numerical Analysis; Optimization; Data Analysis.
          \item \textbf{Bachelor's thesis:} \emph{Ewens Sampling Formula and its Applications to the Study of Population Biodiversity}, supervised by Prof. Emanuele Dolera.
        \end{itemize}}


\newpage
%----------------------------------------------------------------------------------
% Teaching experience
%----------------------------------------------------------------------------------
\cvsubsection{Teaching Experience}

\cventry{10/2021 -- 09/2025}%
        {Academic Tutor}%
        {University of Pavia}%
        {Pavia, Italy}%
        {}%
        {Teaching assistant for Calculus in the Engineering Bachelor's program and Probability in the Artificial Intelligence and Mathematics Bachelor's programs. Supervisors: Prof. Elisabetta Rocca, Prof. Abramo Agosti, Prof. Emanuele Dolera, and Prof. Carlo Orrieri.}

\cventry{10/2023 -- 12/2023}%
        {Lecturer -- Advanced Computational Statistics}%
        {Almo Collegio Borromeo}%
        {Pavia, Italy}%
        {}%
        {Designed and taught the course \emph{Advanced Computational Statistics}, covering theory and applications to real-world data in R. Supervisor: Prof. Emanuele Dolera.}

%----------------------------------------------------------------------------------
% Advanced schools and training
%----------------------------------------------------------------------------------
\cvsubsection{Advanced Schools and Training}

% 2026
\school
  {2026}
  {Jul}
  {Causality and Graphical Models Summer School}
  {Bocconi--StatML, Como, Italy}

\schoolwithtopics
  {}
  {May}
  {Mathematical Foundations of Machine Learning}
  {CIRM, Vason, Italy}
  {Dynamics, geometry, and theoretical guarantees for neural networks and statistical models from an analytical perspective.}

% 2025
\schoolwithtopics
  {2025}
  {Jul}
  {Summer School in Analysis and Machine Learning}
  {Festum Pi, Chania, Greece}
  {Kinetic theory, stability of optimal transport, and diffusion models.}

\schoolwithtopics
  {}
  {Jun}
  {Theoretical Foundations of Machine Learning}
  {MaLGa Center, University of Genoa, Genoa, Italy}
  {Statistical learning theory, kernel methods, neural networks, optimization, RKHS, convex analysis, and generalization.}

\schoolwithtopics
  {}
  {Apr}
  {Computational Optimal Transport and Missing Values}
  {Bocconi--StatML, Windsor, UK}
  {Computational optimal transport (Gabriel Peyr\'e) and statistical learning with missing values.}

% 2024
\schoolwithtopics
  {2024}
  {Dec}
  {PhD Winter School on Advanced Stochastic Optimization}
  {NTNU, Trondheim, Norway}
  {Mixed-integer stochastic programming, decision-making under uncertainty, distributionally robust optimization, and stochastic dual dynamic programming.}

\schoolwithtopics
  {}
  {Jun}
  {2nd Copenhagen PhD School of Stochastic Programming}
  {University of Copenhagen, Copenhagen, Denmark}
  {Stochastic programming, multistage models, bounding techniques, scenario generation, and decision-dependent uncertainty.}

% 2020
\schoolwithtopics
  {2020}
  {Sep}
  {Intensive School in Data Science}
  {ISAGS, University of Pavia, Pavia, Italy}
  {Machine learning and applications in chemistry, genomics, and neuroscience.}

\newpage

\section{Research}

\cvsubsection{Research Interests}

I am interested in \textbf{optimal transport}, especially in the use of tools from \emph{calculus of variations, gradient flows and differential geometry} to study problems arising in statistics, optimization, and machine learning.

%----------------------------------------------------------------------------------
% Current projects
%----------------------------------------------------------------------------------

\cvsubsection{Current Research Projects}

\begin{itemize}
    \item \emph{Sinkhorn Propagation on Graphs}, joint with Hugo Lavenant (Bocconi University). 
    We study a variational propagation problem on graphs involving Sinkhorn divergences, using variational methods, gradient-flow formulations, and numerical algorithms.

    \item \emph{Bayes Rule via Entropic Approximation of the Knothe--Rosenblatt Rearrangement}, joint with Carlo Ciliberto (UCL) and Giulia Luise (UCL/Microsoft Research). 
    We study entropic approximations of the Knothe–Rosenblatt rearrangement for posterior sampling in Bayesian inference.
\end{itemize}

%----------------------------------------------------------------------------------
% Publications
%----------------------------------------------------------------------------------
\cvsubsection{Publications and Preprints}

\cvitem{[1]}{Gianluca Covini, Denis Antipov, Carola Doerr. \emph{Enhancing Parameter Control Policies with State Information}. Proceedings of the Foundations of Genetic Algorithms (FOGA 2025), Leiden, Netherlands, 2025. \href{https://arxiv.org/abs/2507.08368}{arXiv:2507.08368}.}

%----------------------------------------------------------------------------------
% Talks and presentations
%----------------------------------------------------------------------------------
\cvsubsection{Talks and Presentations}

\cventry{Feb 2025}%
        {Conference Presentation}%
        {ROADEF 2025 -- Conference of the French Operations Research Society}%
        {Champs-sur-Marne, France}%
        {}%
        {Presented master's thesis research on dynamic parameter policies for randomized local search on the LeadingOnes problem. Abstract published in the \href{https://roadef2025.org/wp-content/uploads/2025/02/ROADEF2025_resumes.pdf}{ROADEF 2025 Book of Abstracts}.}

\cventry{Jan 2025}%
        {Seminar Talk}%
        {WIAS Berlin, Seminar Series ``Modern Methods in Applied Stochastics and Nonparametric Statistics''}%
        {Online}%
        {}%
        {Presented the paper by Lambert et al., \emph{Variational Inference via Wasserstein Gradient Flows}, in a public seminar of the WIAS research group Stochastic Algorithms and Nonparametric Statistics as part of a PhD interview process.}

\cvsubsection{Software}

\cvitem{}{
  \textbf{\href{https://github.com/gianlucacovini/SlicedWasserstein.jl}{SlicedWasserstein.jl}},
  a registered Julia package for sliced Wasserstein distances.
  Author and maintainer.
}

\newpage
%----------------------------------------------------------------------------------
% Research experience
%----------------------------------------------------------------------------------
\cvsubsection{Undergraduate Research Experience}

\cventry{10/2024 -- 12/2024}%
        {Survey on Distributionally Robust Optimization}%
        {Remote collaboration}%
        {}%
        {}%
        {\begin{itemize}
          \item Informal collaboration on \emph{submodular functions for distributionally robust optimization}.
          \item \textbf{Supervisors:} Prof. Angelos Georghiou (University of Cyprus) and Prof. Rosario Paradiso (VU Amsterdam).
          \item \textbf{Outcome:} \href{https://gianlucacovini.github.io/assets/files/Reports/DRO_report.pdf}{survey report}.
        \end{itemize}}

\cventry{07/2024 -- 08/2024}%
        {Statistics Summer Research Intern}%
        {Statistical Laboratory, University of Cambridge}%
        {Cambridge, UK}%
        {}%
        {\begin{itemize}
          \item Worked on the study of statistical properties of stochastic optimization problems, in the context of causal statistics.
          \item \textbf{Supervisors:} Prof. Qingyuan Zhao and Tobias Freidling.
          \item \textbf{Outcome:} \href{https://gianlucacovini.github.io/assets/files/Reports/stat_opt_report.pdf}{research report}.
        \end{itemize}}

\cventry{03/2024 -- 09/2024}%
        {Research Intern in Operations Research}%
        {LIP6 -- Sorbonne Universit\'e/CNRS}%
        {Paris, France}%
        {}%
        {\begin{itemize}
          \item Conducted research on dynamic algorithm configuration, developing optimal parameter policies for genetic algorithms.
          \item \textbf{Supervisor:} Prof. Carola Doerr.
          \item \textbf{Outcomes:} \href{https://unitesi.unipv.it/handle/20.500.14239/28559}{Master's thesis}; \href{https://www.arxiv.org/abs/2507.08368}{conference paper}.
        \end{itemize}}

\cventry{08/2023 -- 03/2024}%
        {Machine Learning Researcher}%
        {Sphaera}%
        {Hybrid}%
        {}%
        {\begin{itemize}
          \item Developed a player-tracking algorithm for five-a-side football using computer vision and deep-learning tools.
          \item \textbf{Supervisors:} Dr. Mirko Messori and Dr. Giuseppe Roberto Marseglia.
          \item \textbf{Outcome:} \href{https://gianlucacovini.github.io/assets/files/Reports/Relazione_Sphaera_compressed.pdf}{research report}; the resulting implementation is proprietary.
        \end{itemize}}

\section{Recognition}
%----------------------------------------------------------------------------------
% Honors and awards
%----------------------------------------------------------------------------------
\cvsubsection{Scholarships, Honors and Awards}

\cvitem{2024--2026}{\textbf{Selected funded participation} in advanced schools and workshops, including Mathematical Foundations of Machine Learning by CIRM, StatML -- Bocconi Spring School, Festum Pi, Applied Mathematics School at KAUST, PhD School in Stochastic Programming at the University of Copenhagen.}

\cvitem{2025}{\textbf{Full PhD Scholarship}, Bocconi University.}

\cvitem{2024}{\textbf{Merit-Based Scholarship}, Associazione Alunni Almo Collegio Borromeo.}

\cvitem{2024}{\textbf{Fully funded research stay}, Corpus Christi College, University of Cambridge.}

\cvitem{2024}{\textbf{Erasmus+ Traineeship Grant} for research internship at LIP6, Sorbonne Universit\'e/CNRS, Paris.}

\cvitem{2024}{\textbf{Research residence}, Maison de l'Italie, Cit\'e Internationale Universitaire de Paris.}

\newpage

%----------------------------------------------------------------------------------
% Certifications
%----------------------------------------------------------------------------------
\cvsubsection{Certifications}

\cvitem{Oct 2024}{\textbf{TOEFL iBT 106/120 (C1)}, ETS.}

\cvitem{Oct 2024}{\textbf{GRE General Test}, ETS: Quantitative 168, Verbal 162.}

\cvitem{}{\textbf{Additional certifications:} Getting Started with Deep Learning (NVIDIA, 2023); IBM Data Science (Coursera, 2021); DELF B1 (Minist\`ere de l'\'Education Nationale, 2016).}

\section{Skills}

%----------------------------------------------------------------------------------
% Languages
%----------------------------------------------------------------------------------
\cvsubsection{Languages}

\cvitemwithcomment{Italian}{Native}{}
\cvitemwithcomment{English}{C1}{TOEFL iBT 106/120.}
\cvitemwithcomment{French}{B1}{DELF B1.}

%----------------------------------------------------------------------------------
% Computer skills
%----------------------------------------------------------------------------------
\cvsubsection{Computer Skills}

\cvdoubleitem{Programming}{Python, Julia, R, MATLAB}{Scientific computing}{NumPy, Pandas, PyTorch, OpenCV, Matplotlib}
\cvdoubleitem{Optimization}{Pyomo, Gurobi, CPLEX}{Tools}{Git, \LaTeX, Linux, basic HPC usage}
\cvdoubleitem{Other}{Multiprocessing, Excel, WordPress}{Cloud}{Basic AWS usage}

%----------------------------------------------------------------------------------
% Professional and organizational experience
%----------------------------------------------------------------------------------
\section{Service and Additional Experience}

\tlcventry{2026/2}{2024/5}%
        {Member of the Scientific Committee}%
        {\href{https://www.alumnitaramelli.it/}{Associazione Alumni Taramelli}}%
        {}%
        {}%
        {Served on the scientific committee of a project for secondary-school students.}

\tlcventry{2022/10}{2023/10}%
        {Auditor \& Data Analyst}%
        {\href{https://jeitaly.org/}{JE Italy}}%
        {}%
        {}%
        {Monitored and analyzed confederation data; provided audit consulting services for junior enterprises.}

\tlcventry{2021/5}{2023/9}%
        {IT Consultant}%
        {\href{https://jecopavia.it/}{JECO Pavia}}%
        {Pavia, Italy}%
        {}%
        {Data management and digitalization projects for SMEs. As \emph{Head of IT} (Sep 2021 -- Oct 2022), managed area members and annual strategy planning using OKRs.}

\tlcventry{2022/7}{2022/9}%
        {Volunteer}%
        {Sant'Egidio -- Youth for Peace}%
        {Pavia, Italy}%
        {}%
        {Organized recreational activities for children in difficult situations and activities aimed at countering school dropout.}

\tlcventry{2020/10}{2021/9}%
        {Activity Manager}%
        {Entrepreneurship Club Pavia}%
        {Pavia, Italy}%
        {}%
        {Organized public events with entrepreneurs and start-up founders; managed internal activities.}

\tlcventry{2018/10}{2021/9}%
        {Co-Founder and Board Member}%
        {\href{https://www.themostmaiourm.aecserviziweb.com/}{The Most Maiorum}}%
        {Pavia, Italy}%
        {}%
        {Organized cultural and charity events.}

%----------------------------------------------------------------------------------
% References
%----------------------------------------------------------------------------------
%\section{References}

%\cvitem{}{Available upon request.}

% For job applications in the EU/Italy, you may optionally add the following privacy statement.
% For a public academic webpage, I would usually omit it.
%

\enlargethispage{\baselineskip}

\vfill
\noindent
{\scriptsize
\textit{I consent to the processing of my personal data for recruitment purposes in accordance with Regulation (EU) 2016/679 (GDPR).}
\hfill
Last updated: \today
}

\end{document}
